The Astropy Project

### 2017-12-08 main.tex
Address comments from Adrian

The \package{astropy.modeling} subpackage provides a framework for representing
analytical models and performing model evaluation and parameter fitting. Models and
fitters are independent of each other: a model can be fit with different
fitters and new fitters can be added without changing existing models. The
framework is designed to be flexible and easily extensible. The goal is to have
a rich set of models but also make it easy to create new ones if necessary. The
modeling framework is used in a variety of data analysis tools and is the basis
for the Generalized World Coordinate System (GWCS)
package.\footnote{\url{https://github.com/spacetelescope/gwcs}}

>>>>

The \package{astropy.modeling} subpackage provides a framework for representing
analytical models and performing model evaluation and parameter fitting.
The main motivation for this functionality was to create a framework that
allows arbitrary combination of models to support the Generalized World
Coordinate System (GWCS) package.\footnote{\url{https://github.com/spacetelescope/gwcs}}
The current FITS WCS specification lacks the flexibility to represent
arbitrary distortions and does not meet the needs of many types of current instrumentation.
The fact that the \astropypkg modeling framework now supports propagating
units also makes it a useful tool for representing and fitting astrophysical
models within data analysis tools.

Models and fitters are independent of each other: a model can be fit with different
fitters and new fitters can be added without changing existing models. The
framework is designed to be flexible and easily extensible. The goal is to have
a rich set of models, but to also facilitate creating new ones, if necessary.
